FraCaS: 80 percent complete

### 2019-02-15 paper2018/paper.tex
intro additions

\begin{itemize}
	\item[] \textbf{Premise:} A man selling donuts to a customer during a world
exhibition event held in the city of Angeles.
\item[] \textbf{Hypothesis:} A woman drinks her coffee in a small cafe.
\item[] \textbf{Label:} Contradiction

\end{itemize}

\begin{itemize}

\item[\textbf{P1}] A Scandinavian won the Nobel Prize.

	\item[\textbf{P2}]	Every Swede is  Scandinavian.

	\item[\textbf{H.}] Did a Swede win the Nobel prize?

	\item[\textbf{H.}] A Swede won the Nobel prize.

\item[\textbf{Label}] 	YES [FraCaS 173] 	\end{itemize}

@@

\begin{itemize}

\item[\textbf{P1}]	Bill spoke to everyone that John did.

	\item[\textbf{P2}]		John spoke to Mary.

	\item[\textbf{H.}] 	Did Bill speak to Mary?

	\item[\textbf{H.}] 	Bill spoke to Mary.

\item[\textbf{Label}] 	UNK [FraCaS 065] 	\end{itemize}

In this paper, we concentrate on this sort of fine-grained reasoning. In particular, we present the first system that deals with the sections on ellipsis and anaphora in the FraCaS and has both the most coverage, as well as accuracy compared to other logical approaches. More specifically, the contributions of the paper are:

\paragraph{Contributions}

@@

\paragraph{Adjectives}
In our system, we interpret gradable adjectives using a pair of a
measure $m : objects → Z$ and and a threshold $τ : Z$, where $Z$ is
treated as an abstract ordered ring by Coq. (This structure has no
dynamic aspect in our model, and thus is entirely handled within Coq.)
For subsective adjectives, $τ$ will additionally depend on the class
of the object in question. This structure has the benefit that
opposite adjectives can be easily represented (measures are opposites
$∀x. m_1 x = -m_2 x$ and thresholds do not overlap $τ_1 + τ_2 > 0$).
\todo{reference to this view in the litterature}.  Additionally,
adjectival phrases, as present in the FraCaS suite, are interpreted as
linear inequations in $Z$. Solving systems of such inequations is
decidable. Indeed, the tactic that Coq offers for this purpose can
solve all such problems in the FraCaS suite, automatically.

>>>>

\begin{lingex}
\item An SNLI example \\
\textbf{P}  A  man selling donuts to a customer during a world
exhibition event held in the city of Angeles. \\
 \textbf{H}  A woman drinks her coffee in a small cafe.\\
\textbf{Label: Contradiction}
\end{lingex}

\begin{lingex}
\item An example from FraCaS\\

\textbf{P1}] A Scandinavian won the Nobel Prize.\\
\textbf{P2}	Every Swede is  Scandinavian.\\
\textbf{Q}  Did a Swede win the Nobel prize? \\
\textbf{H} A Swede won the Nobel prize.\\
\textbf{Label: Yes} [FraCaS 173]
\end{lingex}

@@

\begin{lingex}

\item An example from FraCaS involving fine-grained reasoning\\
\textbf{P1}	Bill spoke to everyone that John did.	\\	
\textbf{P2}	John spoke to Mary.	\\
\textbf{Q} 	Did Bill speak to Mary?\\
\textbf{H} 	Bill spoke to Mary.\\
\textbf{Label:	UNK} [FraCaS 065] 	\end{lingex}

For this reason, and despite the dominance of DL approaches in pretty much all NLP tasks, logical approaches have been continuing to be developed and evaluated on datasets like the FraCaS test suite and the SICK dataset \cite{marelli:2014}.  \citet{bernardy:2017}  define  a correspondence between abstract syntax parse trees of the FraCas examples, parsed using the Grammatical Framework (GF, \citet{Ranta:GF}), and modern type-theoretic semantics that are output in the Coq proof assistant (the FraCoq system).  The accuracy is 0.85 for 5 ections of the FraCaS test suite. The \textsc{Langpro} system presented by \citet{abzianidze:2017} is based on a Natural Logic tableau theorem prover. It achieves an accuracy of .82 on the SICK dataset.

In this paper, we concentrate on this sort of fine-grained, logical reasoning. In particular, we present the first system that deals with the sections on ellipsis and anaphora in the FraCaS test suite and has both the best coverage, as well as accuracy compared to other logical approaches. More specifically, the contributions of the paper are:

@@

\paragraph{Adjectives}
In our system, we interpret gradable adjectives using a pair of a
measure $m : objects → Z$ and and a threshold $τ : Z$, where $Z$ is
treated as an abstract ordered ring by Coq. (This structure has no
dynamic aspect in our model, and thus is entirely handled within Coq.)
For subsective adjectives, $τ$ will additionally depend on the class
of the object in question. This structure has the benefit that
opposite adjectives can be easily represented (measures are opposites
$∀x. m_1 x = -m_2 x$ and thresholds do not overlap $τ_1 + τ_2 > 0$). Formalization aside, this idea is reminiscent of degree-based approaches to gradable adjectives like \citet{Cresswell:1976,Heim:1985,Kennedy:2007}.   Additionally,
adjectival phrases, as present in the FraCaS suite, are interpreted as
linear inequations in $Z$. Solving systems of such inequations is
decidable. Indeed, the tactic that Coq offers for this purpose can
solve all such problems in the FraCaS suite, automatically.
